EdEntrePres

### 2014-12-02 Presentation/EdEntrePres.Rmd
Reorganized repository and created histogram
Created interactive and static histograms

## Distribution of Perception Differences

```{r}
hist(D4$mean)

```
## Slide with R Code and Output

```{r}
summary(cars)
```

@@

```{r, echo=FALSE}
plot(cars)
```

>>>>

## Distribution of Perception Differences
```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)

D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)

## Slide with R Code and Output

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

D4 %>% 
  ggvis(~mean, fill := "#2c7fb8") %>% 
  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
                   center = input_slider(0, 2, step = 0.05, label = "center"))

@@

```{r, echo=FALSE}
